The Talking Heads Experiment

### 2015-04-08 chap3/chap3.tex
fixes

A first frame of reference is based on
the absolute minima and maxima of the values 
on a sensory channel. This can be used to do 
{\itshape sensor-oriented scaling}. For example, 
the image map captured by the camera
contains 320 \times 240 pixels, which means 
that the horizontal position (HPOS) has a value between
0 and 320 and the vertical position (VPOS) has a value 
between 0 and 240. Both values can be scaled to fall between 
0.0 and 1.0 so that they become uniform with respect to 
other sensory channels. Given a value $x$ and a 
$min$ and $max$ value, then the scaled value is 
$x' = {(x - min)}/{(max - min)}$. 
Thus the sensed value of HPOS=200 becomes
HPOS=0.62 after scaling .

>>>>

A first frame of reference is based on
the absolute minima and maxima of the values 
on a sensory channel. This can be used to do 
{\itshape sensor-oriented scaling}. For example, 
the image map captured by the camera
contains 320 $\times$ 240 pixels, which means 
that the horizontal position (HPOS) has a value between
0 and 320 and the vertical position (VPOS) has a value 
between 0 and 240. Both values can be scaled to fall between 
0.0 and 1.0 so that they become uniform with respect to 
other sensory channels. Given a value $x$ and a 
$min$ and $max$ value, then the scaled value is 
$x' = {(x - min)}/{(max - min)}$. 
Thus the sensed value of HPOS=200 becomes
HPOS=0.62 after scaling .
